\newacronym[long=natural language processing]{nlp}{NLP}{Natural Language Processing}
\newacronym[long=large language model,longplural=large language models]{llm}{LLM}{Large Language Model}
\newacronym[long=business process management]{bpm}{BPM}{Business Process Management}
\newacronym{bpmn}{BPMN}{Business Process Modeling Notation}
\newacronym[long=standard operating procedure]{sop}{SOP}{Standard Operating Procedure}
\newacronym[long=user interface]{ui}{UI}{User Interface}
\newacronym{json}{JSON}{JavaScript Object Notation}
\newacronym[long=proof of concept]{poc}{POC}{Proof of Concept}
\newacronym{tum}{TUM}{Technical University of Munich}
\newacronym{kpi}{KPI}{Key Performance Indicator}
\newacronym{id}{ID}{Identifier}
\newacronym{gpt}{GPT}{Generative Pretrained Transformer}
\newacronym{btp}{BTP}{Business Technology Platform}


\newglossaryentry{sap}{
    name=SAP,
    first={SAP},
    description={is a German multinational software corporation that provides businesses with the necessary tools to manage various operations and customer relations. The company's primary product is its enterprise resource planning (ERP) software, which allows organizations to manage business operations across procurement, manufacturing, service, sales, finance, and HR departments. In addition, SAP also offers cloud-based data services, machine learning, business process management (BPM), and analytics, among other services.}
}

\newglossaryentry{signavio}{
    name={SAP Signavio},
    first={Signavio},
    description={is an \gls{sap} sub-brand, providing a suite of business process management tools designed to streamline business processes, reduce operational complexity, and ensure compliance. It allows businesses to model, analyze, optimize, and execute business process workflows. This platform helps organizations to understand and improve their business processes, make data-driven decisions, and translate business strategy into operational reality.}
}

\newglossaryentry{signavio-workspace}{
    name=Signavio workspace,
    first={Signavio workspace},
    description={is a designated virtual area within the Signavio software platform where users can create, manage, and collaborate on business process models and related projects.}
}

\newglossaryentry{process discovery algorithm}{
    name=process discovery algorithm,
    first=process discovery algorithm,
    description={is a chronological sequence of activities representing one instance of a process execution. It aids in identifying patterns for improving business processes.}
}

\newglossaryentry{trace}{
    name=trace,
    first=trace,
    description={is a chronological sequence of activities or events recorded from the initiation to the termination of an executed instance of a process. Each trace is an instance of a process sequence, representing the path taken through the process. It often serves as a valuable source of information for process analysis, process mining, and performance evaluation. The collected set of traces forms an \gls{event log}.}
}

\newglossaryentry{event log}{
    name=event log,
    first=event log,
    description={is a recorded sequence of events or activities related to individual process instances. It typically consists of a Case\acs{id}, an activity, and a timestamp. It provides a detailed record of activities, resources involved, and outcomes, serving as a primary data source for process discovery, analysis, and improvement.}
}


% \newglossaryentry{word embedding}{
%     name={word embedding},
%     first={word embedding},
%     description={A word embedding is a numerical representation (often a high dimensional vector) of a word that tries to capture its meaning. This representation can be used for \glsdesc{ml} algorithms and to perform opertations on it (e.g., distance measures via cosine similarity) \citep{almeida-2019-word-embeddings-survey}.}
% }
% \newglossaryentry{embedding}{
%     name=embedding,
%     first=embedding,
%     description={Embeddings in general can not only represent a word, but also a whole sentence or text. The functionality however is similar to that of \glspl{word embedding}}.
% }
% \newglossaryentry{overfitting}{
%     name=overfitting,
%     first=overfitting,
%     description={Overfitting occurs when a machine learning model learns the training data too well and becomes overly specialized to it. This can cause the model to perform poorly on new, unseen data. Overfitting can be prevented through techniques such as regularization, cross-validation, or using a larger and more diverse data set \citep{salman-2019-overfitting}.}
% }